Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide

### 2024-10-28 doc/presentations/defensio/defense.tex
first real draft of densio

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  Die vorliegenden LaTeX-Folien stehen Mitarbeiter*innen und Studierenden der Universität Wien
%%  zur Verfügung und sind ausschließlich zur Verwendung in Forschung und Lehre der Universität  
%%  Wien vorgesehen. Das Copyright der LaTeX-Vorlagen liegt bei der Universität Wien.
%%
%%  These LaTeX slides are available to employees and students of the University of Vienna 
%%  and are intended exclusively for use in research and teaching at the University of Vienna. 
%%  The copyright of the LaTeX templates is held by the University of Vienna.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169

@@

	%% ====== title page ======
	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

\usepackage{siunitx}
\usepackage{chemformula}

@@

%% ====== Slides ======
%TODO: - read aqua/good recipe/mars paper
%01. title slide 
	% - aufhänger
	% - AI and PV
	% - Lab or Computer 
%02. agenda
	% - more like process  from beginning to finish
%03. background info
	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
\begin{textFrame}
	{Copper indium gallium selenide solar cell}
	{1}{}
%	\begin{itemize}
%		\item lorem
%		\item ipsum
%		\item \dots
%	\end{itemize}
\begin{table}[tbh]
	\small
    \center
%	\iffalse
	\resizebox{\textwidth}{!}{
		\begin{tabular}{cccccc}
			\hline
			\hline
			Material&   Type&    Band Gap [eV]&    $\lambda$ [nm]&    Abs. coef. $\alpha$ [cm$^{-1}$]    &Penetration Depth [$\mu$m]\\
			\hline
			c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
			c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
			c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
			a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
			CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
			GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
			\hline
			\hline
		\end{tabular}
	}
    \caption{Photonic properties of several established PV materials (\cite{mertens2020photovoltaik})}
	\label{tab:cigs:alpha}
%	\fi
%
	\resizebox{.45\textwidth}{!}{
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&   Band Gap [\si{eV}{}]\\
        \hline
		\ch{CuInSe2}&  1.04\\
		\ch{CuInS2}&  1.5\\
		\ch{CuGaSe2}&  1.7\\
		\ch{CuGaS2}&  1.55\\
        \hline\hline
    \end{tabular}
}
    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
\end{table}
\end{textFrame}

\begin{graphicsFrame}{Copper Indium Gallium Sulfide}{}{0.37}{left}{cigs}{Rau, Schock (2013) "Solar Cells"}
		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\end{itemize}
\end{graphicsFrame}

\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}

\end{graphicsFrame}
%04. hypothesis 
%05. manual methods
	% - precursor solution preparation 
		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
\begin{frame}{test}

\begin{table}[h]
	\center
	\caption{Composition of different buthanolic solutions}
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}
\end{frame}

	% - doctor blading = tape castig 
	% - calcination 
\begin{frame}{Tape casting and Calcination}
	\begin{itemize}
		\item doctor blading construction 
		\item calcination infos (max temperatur, heating rate)
	\end{itemize}
\end{frame}
	% - sputtering contacts
	% - measuring current-voltage characteristics
\begin{frame}{Sputtering and I-V measurement}
	\begin{itemize}
		\item Aluminium Contact through mask
		\item Silver paste
	\end{itemize}
\end{frame}
%06. computational pipeline 
	% - PSO + MARS = EMMA
	% PSO https://doi.org/10.1109/CEC.2010.5586165
\begin{frame}{EMMA = PSO + MARS}
	\begin{itemize}
		\item Particle Swarm Opitimisation 
	\end{itemize}
\end{frame}
%07. results measuring 
	% - SEM % check which sample 
\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
		\begin{itemize}
			\item (a) first recipe on FTO
			\item (b) 10 layers on steel
			\item (c) cross section of 5 layers on FTO
			\item (d) side view of scratched layer on steel
		\end{itemize}
\end{graphicsFrame}

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats
	\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
%    \caption{Post EMMA vergleich}
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
}
	\vspace{1em}
    %
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}

%10. summary 
	% - created ZrO2
	% - optimized with EMMA
	% - double checked with stats
%11. conclusion 
%12. end

>>>>

%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  Die vorliegenden LaTeX-Folien stehen Mitarbeiter*innen und Studierenden der Universität Wien
%%  zur Verfügung und sind ausschließlich zur Verwendung in Forschung und Lehre der Universität  
%%  Wien vorgesehen. Das Copyright der LaTeX-Vorlagen liegt bei der Universität Wien.
%%
%%  These LaTeX slides are available to employees and students of the University of Vienna 
%%  and are intended exclusively for use in research and teaching at the University of Vienna. 
%%  The copyright of the LaTeX templates is held by the University of Vienna.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	%% ====== title page ======
	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

\usepackage{siunitx}
\usepackage{chemformula}
\usepackage{upgreek}

@@

%% ====== Slides ======
%TODO: - read aqua/good recipe/mars paper
%01. title slide 
	% - aufhänger
	% - AI and PV
	% - Lab or Computer 
%02. agenda
\begin{frame}{Agenda}
	\vspace{2em}
	\begin{itemize}
		\item Motivation: CIGS substrate
		\item Methods: recipe and sample preparation
		\item Calculation: PSO and data pipeline
		\item Results: materials and optimisation
	\end{itemize}
\end{frame}
	% - more like process  from beginning to finish
%03. background info
	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
\begin{graphicsFrame}{Copper Indium Gallium Selenide (CIGS)}{}{0.37}{left}{cigs}{U. Rau, H.W. Schock (2013) "Solar Cells"}
\begin{table}
	\resizebox{.95\textwidth}{!}{
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&   Band Gap [\SI{}{\electronvolt}]\\
        \hline
		\ch{CuInSe2}&  1.04\\
		\ch{CuGaSe2}&  1.7\\
		\ch{CuInS2}&  1.5\\
		\ch{CuGaS2}&  1.55\\
        \hline\hline
    \end{tabular}
}
    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
\end{table}
\end{graphicsFrame}

\iffalse
\begin{textFrame}{Thin Film Solar Cell}{1}{}
%	\begin{itemize}
%		\item lorem
%		\item ipsum
%		\item \dots
%	\end{itemize}
\begin{table}[tbh]
	\small
    \center
	\resizebox{\textwidth}{!}{
		\begin{tabular}{cccccc}
			\hline
			\hline
			Material&   Type&    Band Gap [\SI{}{\electronvolt}]&    $\lambda$ [\SI{}{\nano\meter}]&    Abs. coef. $\upalpha$ [\SI{}{\centi\meter^{-1}}]    &Penetration Depth [\SI{}{\micro\meter}]\\
			\hline
			c-Si&   indirect&   1.12&   600&    4000&    2.5\\
			c-Si&   indirect&   1.12&   1000&    64&    150\\
			c-Si&   indirect&   1.12&   1100&    3.5&    290\\
			a-Si&   direct&      1.7&    600&    40000&  0.25\\
			CdTe&   direct&      1.45&    600&    37000&  0.3\\
			GaAs&   direct&      1.42&    600&    40000&  0.2\\
			\hline
			\hline
		\end{tabular}
	}
    \caption{Photonic properties of several established PV materials (K. Mertens 2015 "Photovoltaik")}
	\label{tab:cigs:alpha}
\end{table}
\end{textFrame}
\fi

\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}
\end{graphicsFrame}

%04. hypothesis 
%05. manual methods
	% - precursor solution preparation 
		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
\begin{frame}{Recipes for Precursor Solutions}
	\begin{figure}
		\includegraphics[width=.79\textwidth]{figures/huetal.png}
	\end{figure}
	\pause
\begin{table}[h]
	\center
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
	%\caption{Composition of different buthanolic solutions}
\end{table}
\end{frame}

	% - doctor blading = tape castig 
	% - calcination 
\begin{frame}{Tape casting and Calcination}
	\begin{figure}
		\center
		\includegraphics[width=.65\textwidth]{figures/tc.jpg}
	\end{figure}
\end{frame}
%	\begin{itemize}
%		\item doctor blading construction 
%		\item calcination infos (max temperatur, heating rate)
%	\end{itemize}
%\end{frame}
	% - sputtering contacts
	% - measuring current-voltage characteristics
\begin{frame}{Sputtering and I-V measurement}
	\begin{figure}
		\includegraphics<1>[width=.63\textwidth]{figures/sample1.jpg}
		\includegraphics<2>[width=.63\textwidth]{figures/sample2.jpg}
		\includegraphics<3>[width=.63\textwidth]{figures/sample3.jpg}
	\end{figure}
\end{frame}

%06. computational pipeline 
\begin{frame}{Pin Hole Density and Leakage Current}
	\vspace{2em}
	\begin{itemize}
		\item Pin Hole Density 
			\begin{itemize}
				\item $
%	\rho = \frac{n_{-}}{(n_{-} + n_{+})}
	\rho = \sum_i^N \frac{s_i}{N}
					$
				\item $
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
					$
			\end{itemize}
	\vspace{0.5em}
		\item Leakage Current 
			\begin{itemize}
				\item $
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	$
			\end{itemize}
	\end{itemize}
\end{frame}
	% - PSO + MARS = EMMA
	% PSO https://doi.org/10.1109/CEC.2010.5586165
\begin{graphicsFrame}{Particle Swarm Optimisation}{}{0.37}{right}{swarm}{}
	\vspace{2em}
	\begin{itemize}
		\item ispired by bird flocks and fish schools %# swarm intelligence
		\item iterative process % nice bcs sample prep takes long time 
		\item particles: 
			\begin{itemize}
				\item position 
				\item velocity
			\end{itemize}
		\item update model
		\item R package \texttt{emma} 
	\end{itemize}
\end{graphicsFrame}

\begin{frame}{PSO variables}
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
		$c_{zr}$ [\SI{22}{\milli\mol/\liter}]	&$n_L$	&$T_{C}$[\SI{}{\degreeCelsius}]	&$v_{C}$[\SI{}{\milli\meter/\second}]	&$T_{cal}$[\SI{}{\degreeCelsius}]	&$v_{cal}$[\SI{}{\degreeCelsius/\hour}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}
\end{frame}

%	\begin{itemize}
%		\item Aluminium Contact through mask
%		\item Silver paste
%	\end{itemize}
%\end{frame}
%07. results measuring 
	% - SEM % check which sample 
\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
		\begin{itemize}
			\item (a) first recipe on FTO
			\item (b) 10 layers on steel
			\item (c) cross section of 5 layers on FTO
			\item (d) side view of scratched layer on steel
		\end{itemize}
\end{graphicsFrame}

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
\begin{frame}{Pin Hole Density}\begin{figure}\includegraphics[width=.66\textwidth]{figures/phd.png}\end{figure}\end{frame}
\begin{frame}{Leakage Current}\begin{figure}\includegraphics[width=.66\textwidth]{figures/leakage.png}\end{figure}\end{frame}
\begin{frame}{PSO generations}\begin{figure}\includegraphics[width=.96\textwidth]{figures/emma-gen.png}\end{figure}\end{frame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
%\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats

\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc }
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)\\
    \hline
		PSO&   \textbf{10}& 171\\
        LR&    13& 250\\
        KRR &17 &548 \\
        SVM& 15&  415\\
    \hline\hline
	\end{tabular}
%}
	\pause
%	\vspace{1em}
%	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)\\
    \hline
		PSO&   \textbf{0.14}&   0.03\\
        LR&    0.19&   0.06\\
        KRR &0.25 &0.12 \\
        SVM &0.23 &0.13 \\
    \hline\hline
	\end{tabular}
%}
%    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}

\iffalse
\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
}
	\vspace{1em}
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}
\fi

%10. summary 
\begin{frame}{Summary}
	\vspace{2em}
	\begin{itemize}
		\item new recipe for dense \ch{ZrO2}
			\vspace{.5em}
		\item optimzed method with PSO
	\end{itemize}
\end{frame}
	% - created ZrO2
	% - optimized with EMMA
	% - double checked with stats
%11. conclusion 
%12. end
